---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Tian Yi Zhang
thanks: "Code and data supporting this paper are available at: AOIWDJAWOIDJ"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
# Load the required packages for this paper
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr) # for kable()
library(ggplot2) # for graphs
```

# Introduction

The usage of contraception has become an important part of modern society.
Various contraceptive methods have been invented throughout the years to aid
couples in their family planning efforts. These contraceptive methods range from
hormonal methods and intrauterine methods to barrier methods, providing many
options for both male and female users. Notably, according to the Centers for
Disease Control and Prevention, the barrier method known as condom was the most 
popular male contraceptive used in the United States a few years ago,
with it being around 8.7% of total contraceptives used [@citeCDC].
This is also the case in the country of Kenya, with around 1% of the surveyed
individuals reporting to have used condoms, as denoted in the 1998 DHS
report [@citeDHS].

Another interesting statistic in the studies mentioned above are the high
usage rates of female hormonal contraceptives. 12.6% of contraceptive methods
used in the United States are of the oral hormonal type [@citeCDC], and around
9% of surveyees in Kenya report using oral contraceptives as well [@citeDHS].
This statistic is perplexing in that the usage rate of hormonal contraceptives
are rather high despite the noticeable side effects:
Various studies have suggested in the past that female contraceptives often
lead to high-risk side effects. For example, the U.S. Department of Health &
Human Services notes that oral contraceptives that rely on hormonal controls
can lead to higher blood pressure and more blood clots [@citeDHH]. As such, one
would wonder why male contraceptives do not see more wide usage despite a
relative lack of harmful side effects in comparison to female hormonal
contraceptives.

This paper attempts to analyze potential reasons for the relative lack of
condom usage as a contraceptive method in Kenya utilizing statistics presented
in the 1998 DHS final report on Kenya [@citeDHS]. Specifically, the paper focuses
on finding a, of lack thereof, relationship between the age, geographical
location, and the knowledge of condom(TODO)

WRITE SOMETHING ABOUT FINDINGS; WRITE SOMETHING ABOUT THE STURCTURE OF THE PAPER

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point). 



# Data

## Raw Data Origin and DHS Methodology

The dataset used in this paper is obtained from the PDF "FR102", titled 
"Kenya Demographic and Healthy Survey 1998" and published in 1998 by
the Demographic and Health Surveys Program.^[The PDF can be obtained at
https://dhsprogram.com/publications/publication-fr102-dhs-final-reports.cfm?csSearch=456440_1.]

The PDF where the dataset is parsed from is a report compiled by the DHS program
using the third Demographic and Health Survey conducted in Kenya, the previous
two of which were conducted in 1989 and 1993. [@citeDHS]. According to the
information provided on the DHS Program website, Standard DHS Surveys are
described as surveys with a sample size that consists of 5000 to 30000
households conducted on a five year cycle [@citeDHS2].
Since there is around a five year gap between each consecutive Kenya DHS
survey, we can safely assume that the PDF report containing the raw data is
a standard DHS survey.

The survey used by the DHS Program was distributed in nearly all districts in
Kenya. While the total population of the districts not included in the survey
only amounts to less than four percent of the country's population, it is still
a substantial percentage of the national population that was not sampled from.
The PDF specified that stratified sampling was used, which greatly
contributes greatly to the increase in precision
of the findings from the survey and generally leads to a sample that better
represents the population than a simple random sampling.
However, it was unclear to the readers what
characteristics or attributes were used to divide the population into strata.
Since it was stated later in the PDF that the survey wished to obtain
"district-level data for planning purposed" [@citeDHS], it should be safe to
assume that the strata were constructed based on geographical locations.
It is also worth noting that the survey included men from age 15 to 54 while
only including women from age 15 to 49. A sufficient justification was not
found for this discrepancy and it may have an impact on the accuracy of the
findings.

According to the DHS report [@citeDHS], the survey questions can be divided
into 14 categories. Of those 14, the following subset of topic is related
to the focus of this paper:

* Background characteristics such as age and education
* Knowledge and use of family planning methods.

The surveys questions were originally constructed fully in English before being
translated into various local languages, and the wording of the questions
were revised several times by local pretest teams before being sent out, 
ensuring that there will not be any inaccuracies or awkward wording present due
to the language barrier.
[@citeDHS]. This is especially important due to the sensitive nature of the
topics asked in the surveys, and helps in making sure that as many
participants answer honestly as possible.

## Dataset Parsing and Cleaning

The raw dataset is parsed using the package `pdftools` [@citePDF]
and the statistical programming language R [@citeR] from 
Table 10.14.1 and Table 10.14.2 on page 170 and 171 of the PDF respectively 
[@citeDHS]. Two tables are parsed instead of one because the tables each present
data on only one gender. Therefore a dataset that combines data from both
genders in order to provide a more accurate analysis. As such,
a new variable, `gender`, is constructed to help distinguish the data between
female and male participants. Additionally, there is an issue in that the rows
of the tables corresponded to different variables; for example, some rows 
contained data for certain age groups while other rows contained data for 
different marital statuses. To simplify the analysis process, only the rows 
pertaining to age groups, education, and provinces were parsed from the PDF.

The dataset is then cleaned using the `janitor` package 
[@citejani] and the `pointblank` [@citePB] package is used to set up validation
tests for the class and the content of the datasets.
Subsequent graphs and tables shown in this paper also utilize the
`tidyverse` [@citetidy] and `knitr` [@citeknitr] packages.

The final datasets---clean_data_age.csv, cleaned_data_province.csv
and cleaned_data_education.csv---showcased
in Table \@ref(tab:showcase1), Table \@ref(tab:showcase2) and 
Table \@ref(tab:showcase3) respectively,
contains the information about the same variables in every column except the 
first, which is the column that denotes either the age, province or education. 
The purpose of the other columns are explained in the DHS report [@citeDHS],
summarized as follows:

* gender: male or female
* know_about_condoms: percentage of participants that know about condoms
* public_sector: percentage of participants that cited government-run health
services as their primary source for obtaining condoms
* private_medical_sector: percentage of participants that cited private medical
sources as their primary way for obtaining condoms
* private_pharmacy: percentage of participants that cited private pharmacies as
their primary source for obtaining condoms
* shop: percentage of participants that cited commercial shops as their primary
source for obtaining condoms
* cbd_agent: percentage of participants that cited community-based distribution
agents as their primary source for obtaining condoms
* friends_and_relatives: percentage of participants that cited their friends and
relatives as their primary source for obtaining condoms
* other_sources: percentage of participants that cited other sources as their
primary way for obtaining condoms
* dont_know_a_source: percentage of participants that do not know a source for
obtaining condoms
* number_of_people: number of participants that belong in each category

## Preliminary Analysis

Table \@ref(tab:showcase1) shows that an overwhelming majority of surveyees
know about condoms, with all percentages well over 90%. For women, the 
percentage of surveyees that know about condoms are relatively lower in age
groups 15-19 and 40-49, though there is not a similar trend for men, as more
than 97% of men know about condoms in all age groups surveyed. This difference
could be due to the fact that condom is a male-contraceptive and is thus less
advertised to women. Similarly, Table \@ref(tab:showcase1) shows that a larger
percentage of men know about condoms than women in every single province
survyed, though this difference is minuscule.

```{r showcase1, echo=FALSE, warning=FALSE, message=FALSE}
# Read in the dataset
kenya_condom_age <-
  read_csv(here::here("outputs/data/cleaned_data_age.csv"))

# Create a table that showcases the age dataset
kenya_condom_age |> 
  select(age, gender, know_about_condoms ,public_sector, 
         private_medical_sector) |>
  kable(
    caption = "First 5 columns on percentage of participants, categorized by
    age groups, that know about 
    and/or cite a specific source for condoms, or do not know about condoms",
    col.names = c("Age","Gender","Know About Condoms","Public Sector",
                  "Private Medical Sector"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

```{r showcase2, echo=FALSE, warning=FALSE, message=FALSE}
# Read in the dataset
kenya_condom_province <-
  read_csv(here::here("outputs/data/cleaned_data_province.csv"))

# Create a table that showcases the province dataset
kenya_condom_province |> 
  select(province, gender, know_about_condoms ,public_sector, 
         private_medical_sector) |>
  kable(
    caption = "First 5 columns on percentage of participants, categorized by 
    provinces, that know about 
    and/or cite a specific source for condoms, or do not know about condoms",
    col.names = c("Province","Gender","Know About Condoms","Public Sector",
                  "Private Medical Sector"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

```{r showcase3, echo=FALSE, warning=FALSE, message=FALSE}
# Read in the dataset
kenya_condom_education <-
  read_csv(here::here("outputs/data/cleaned_data_education.csv"))

# Create a table that showcases the education dataset
kenya_condom_education |> 
  select(education, gender, know_about_condoms, public_sector, 
         private_medical_sector) |>
  kable(
    caption = "First 5 columns on percentage of participants, categorized by 
    education level, that know about 
    and/or cite a specific source for condoms, or do not know about condoms",
    col.names = c("Education","Gender","Know About Condoms","Public Sector",
                  "Private Medical Sector"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

The datasets also show that there are more than twice the number of female 
participants than male participants. Note that according to Faria [@citeStati],
the gender ratio in Kenya in 2000 is about 98.6 males per 100 females, meaning
that there is no significant numerical difference between genders in Kenya.
Therefore, the unequal sample size in the dataset could lead to unequal
variances between the male and female samples and would negatively affect the
results of any tests that require the assumption of equal variances.

\newpage

## Knowledge of a source for condom: Age Groups

```{r graph, fig.cap="Percentage of Surveyee Without Knowledge of A Source for Condom versus Age Groups", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_age %>%
  ggplot(aes(x = age, y = dont_know_a_source, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Don't know a source for condom (%)",
       x = "Age Group")
```

We can observe from Figure \@ref(fig:graph) that there is a substantially higher
percentage of women who possess no knowledge of ways to obtain condoms
In all age groups, there are on average twice as many women who do not know 
a source to obtain condoms compared to men. This difference is much more
drastic in the younger population (age 15-19).

Note that the female age group of 50-54 was not included in the sample, thus
leaving no way for us to compare the difference in percentage for that specific
age group.

## Knowledge of a source for condom: Geographical Location

```{r graph2, fig.cap="Percentage of Surveyee Without Knowledge of A Source for Condom versus Provinces", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_province %>%
  ggplot(aes(x = province, y = dont_know_a_source, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Don't know a source for condom (%)",
       x = "Province")
```

Figure \@ref(fig:graph2) plots the percentage of male and female
surveyees without knowledge on a source for condoms in each province 
surveyed and in total.

Similar to the trend shown in Figure \@ref(fig:graph), the difference in
percentage between female and male participants are at the minimum 10%, with
women being far more likely to know no source for condoms.

According to Table 2.4 in the Kenya Population and Housing Census in 2019 
[@citeKPHC], Nairobi, the capital city of Kenya, has a population density of
6247 personnel per square kilometer, dwarfing any other county or province in
Kenya. One hypothesis is that this level of population density and urbanization 
may be a reason as to why the gap between female and male knowledge on condom 
sources is relatively smaller in Nairobi. However, Nyanza, a province
where the population density of its counties range from 393 to 958 personnel
per square kilometer, has a difference in female and male knowledge
on condom sources very similar to Nairobi's.

## Knowledge of a source for condoms: Education Level

```{r graph3, fig.cap="Percentage of Surveyee Without Knowledge of A Source for Condom versus Education Level", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_education %>%
  ggplot(aes(x = education, y = dont_know_a_source, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Don't know a source for condom (%)",
       x = "Education")
```

Figure \@ref(fig:graph3) shows a trend that is similar to the previous two;
a higher percentage of women do not know a source for condoms compared to men.
A notable outlier is when there is a complete lack of education: 
Both female and male surveyees without any education have nearly identical 
level of ignorance regarding ways to obtain condoms.

\newpage

# Results

## Population density and knowledge on condoms

As shown in Figure \@ref(fig:graph2), the difference in ignorance of condom
sources between women and men vary by a significant amount between provinces.
The initial hypothesis presented in this paper is that the difference could be
linked to the population density in each province. However, after reviewing
the Kenya Population Census [@citeKPHC], no apparent pattern is found. Some
provinces with relatively massive population density such as Nairobi have a 
smaller difference in condom source ignorance as hypothesized to be due to its 
greater urbanization. However, other provinces that contain counties with
population density comparable to Nairobi, such as the Coast province, have
a much large difference in condom source ignorance between men and women:
Mombasa,
a county in the Coast province, has the second largest population density
at 5495 personnel per square kilometer, yet the overall gap between
female and male knowledge on condom sources is still relatively large in
the Coast province. On the other hand, Nyanza, a province
where the population density of its counties range from 393 to 958 personnel
per square kilometer, has a difference in female and male knowledge
on condom sources very similar to Nairobi's.
It is unclear as to whether population density plays an
important role in determining the region's ignorance of sources to obtain
condoms.

## Age Group and knowledge on condoms

Figure \@ref(fig:graph) shows that lack of knowledge on a source for condoms
is much higher in the younger age group (age 15 to 19), decreases in older
age groups, and once ago rises in the oldest age groups (age 40 to 49 and
age 50 to 54).

In general, the disparity between percentage
of women and men that do not know a source for condoms remains largely
unaffected by age groups, though is worth noting however that younger surveyees
(people in the age of 15 to 19) have a relatively higher difference in this
regard.
In total, the percentage of women that do not know of a source 
for condoms are 15.1% higher than men.

## Education Level and knowledge on condoms

As demonstrated in Figure \@ref(fig:graph3), a staggeringly high percentage
of women and men with no education have no knowledge on where to obtain
condoms.
The graph also shows that receiving a higher level of
education leads to an overall decrease in condom source ignorance in
both genders. However, the difference in condom source ignorance between
women and men seem to not be correlated to education level, as the difference
in condom source ignorance between genders is lower in both the 'No Education'
and 'Secondary+' levels compared to the 'Primary Incomplete' and
'Primary Complete' levels.

# Discussion

## Level of Variance in Population Density

As discussed in the Results section, we seemingly cannot establish a
relationship between population density of a province and the difference in
condom source ignorance between its female and male residents. The reasoning
is that provinces that contain counties with similar levels of population
density have very difference disparities in the percentage of women and men that
know where to obtain condoms. However, it is important to note that each
province is sectioned into different numbers of counties. A possible connection
that was not analyzed in this paper is the hypothesis that the aforementioned
disparities were caused by the level of variance in population density among
the counties for each province. For example, according to the Kenya Population
Census [@citeKPHC], Nyanza, a province
where the population density of its counties range from 393 to 958 personnel
per square kilometer, has a difference in female and male knowledge
on condom sources very similar to that of the Nairobi province. On the other
hand, the Rift Valley province contains counties with population density 
ranging from 14 to 397 personnel per square kilometer, and the Eastern province
contains counties with population density ranging from 6 to 236 personnel per
square kilometer. In these two provinces which have relatively lower variance in
its counties' population densities, the difference in percentage of women
and men that know sources for condoms are much larger compared to Nyanza, a
province with a higher variance in its counties' population densities. There is
a possibility of correlation in here, and this
direction could prove to be an interesting add-on or extension of this paper.

## Higher percentage of women with no knowledge of condom sources on average

Across all the tables and graphs presented in this paper, it is apparent that
on average, a significantly higher percentage of women have no knowledge
sources for condoms. It is unclear as to why this disparity exists. One possible
reasoning is that condom is a male-contraceptive and thus less advertised to
women.

## Limitations

### Unequal sampling size between genders

As discussed in the beginning of the Data section, in the report conducted by
the DHS Program that is used to extract the raw data for this paper from, there
are more than twice the number of female surveyees than male surveyees, yet,
according to Faria [@citeStati],
the gender ratio in Kenya in 2000 is about 98.6 males per 100 females, meaning
that there is no significant numerical difference between genders in Kenya.
Therefore, there is no feasible justification for this difference in sample
size between genders. This disadvantage could negatively affect the accuracy
of any tests based on the assumption of equal variances.

### Inexplicable lack of data

As showcased in Figure \@ref(fig:graph), there is a lack of data for women in
the age group of 50 to 54 and we could not locate an explanation for it in the
DHS Program report. It could be that there were simply not enough female
surveyees in the age group of 50 to 54; While it was stated in the DHS Program
report [@citeDHS] that it used stratified sampling, the report did not specify
which characteristic the sample was stratified on, leaving no way for us to
figure out the reasoning behind this discrepancy.

### Omission of certain counties and estimation for certain counties

The survey used by the DHS Program was distributed in nearly all districts in
Kenya. While the total population of the districts not included in the survey
only amounts to less than four percent of the country's population, it is still
a substantial percentage of the national population that was not sampled from.

Additionally, the DHS Program report [@citeDHS] noted that due to a drastic
increase in number of counties in the country in the few years prior to the
publication of the report, values for certain variables for some rural counties
were estimated instead. One of the reasons for doing so, as stated in the DHS
Program report, was that these districts were included in the previous two
DHS Program reports of the same nature on Kenya, and thus reliable estimates
could be achieved. It is unclear as to how much these estimates deviate from
the true data or how much effect this has on the overall dataset, but it is
nevertheless a potential source of error that sadly cannot be remedied in the
scope of this paper alone.


\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References


