---
title: "Women in Kenya Severely Lack Knowledge on Source of Condom Supply Across All Age Groups And Provinces"
author: 
  - Tian Yi Zhang
thanks: "Code and data supporting this paper are available at: https://github.com/zhan7818/kenya-condom-knowledge"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The use of contraception is a vital part of modern family planning, yet high risk hormonal contraceptives are curiously more widely used than male contraceptives such as condoms. We obtain data from the 1998 DHS Program report regarding the primary sources for women and men of Kenya to obtain condoms and analyze it using several graphs and tables. The data shows a consistent trend for percentage of women who do not know a source of condom supply to be much higher than men in Kenya regardless of age groups and geographical locations, though higher education levels correlates to increased knowledge in sources for condom supply. Findings suggest an increase in condom advertisement targeted towards women across all age groups and provinces, and an increase in condom advertisement from governement-run healthy services targeted towards poorly educated citizens."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
# Load the required packages for this paper
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr) # for kable()
library(ggplot2) # for graphs
```

# Introduction

The usage of contraception has become an important part of modern society.
Various contraceptive methods have been invented throughout the years to aid
couples in their family planning efforts. These contraceptive methods range from
hormonal methods and intrauterine methods to barrier methods, providing many
options for both male and female users. Notably, according to the Centers for
Disease Control and Prevention, the barrier method known as condom was the most 
popular male contraceptive used in the United States a few years ago,
with it being around 8.7% of total contraceptives used [@citeCDC].
This is also the case in the country of Kenya, with around 1% of the surveyed
individuals reporting to have used condoms, as denoted in the 1998 DHS
report [@citeDHS].

Another interesting statistic in the studies mentioned above are the high
usage rates of female hormonal contraceptives. 12.6% of contraceptive methods
used in the United States are of the oral hormonal type [@citeCDC], and around
9% of surveyees in Kenya report using oral contraceptives as well [@citeDHS].
This statistic is perplexing in that the usage rate of hormonal contraceptives
are rather high despite the noticeable side effects:
Various studies have suggested in the past that female contraceptives often
lead to high-risk side effects. For example, the U.S. Department of Health &
Human Services notes that oral contraceptives that rely on hormonal controls
can lead to higher blood pressure and more blood clots [@citeDHH]. As such, one
would wonder why male contraceptives do not see more wide usage despite a
relative lack of harmful side effects in comparison to female hormonal
contraceptives. A possible hypothesis is that due to it being a contraceptive
meant to be used by men, it is less advertised to women.

This paper attempts to analyze potential reasons for the relative lack of
condom usage as a contraceptive method in Kenya utilizing statistics presented
in the 1998 DHS final report on Kenya [@citeDHS]. Specifically, the paper focuses
on finding a, of lack thereof, relationship between the age, geographical
location, and the knowledge of sources for obtaining condoms.

The remainder of this paper contains analysis on the dataset and the resulting
findings. Section \@ref(data) details the data analysis of this paper. Section
\@ref(raw-data-origin-and-dhs-methodology) discusses the origin of the raw
data used in this paper, and \@ref(dataset-parsing-and-cleaning) details
the extraction process for the dataset. 
Subsequent graphs and tables shown in this paper utilize the
statistical programming language R [@citeR] and the
`tidyverse` [@citetidy], `ggplot2` [@citeggplot2] and `knitr` 
[@citeknitr] packages. 
Section \@ref(results) details the
results from the data analysis, which includes findings on Kenyan women's 
generally higher lack of knowledge of a viable source for obtaining condoms 
compared to men. All limitations and potential extensions
are discussed in Section \@ref(discussion).

# Data

## Raw Data Origin and DHS Methodology

The dataset used in this paper is obtained from the PDF "FR102", titled 
"Kenya Demographic and Healthy Survey 1998" and published in 1998 by
the Demographic and Health Surveys Program.^[The PDF can be obtained at
https://dhsprogram.com/publications/publication-fr102-dhs-final-reports.cfm?csSearch=456440_1.]

The PDF where the dataset is parsed from is a report compiled by the DHS program
using the third Demographic and Health Survey conducted in Kenya, the previous
two of which were conducted in 1989 and 1993. [@citeDHS]. According to the
information provided on the DHS Program website, Standard DHS Surveys are
described as surveys with a sample size that consists of 5000 to 30000
households conducted on a five year cycle [@citeDHS2].
Since there is around a five year gap between each consecutive Kenya DHS
survey, we can safely assume that the PDF report containing the raw data is
a standard DHS survey.

The survey used by the DHS Program was distributed in nearly all districts in
Kenya. While the total population of the districts not included in the survey
only amounts to less than four percent of the country's population, it is still
a substantial percentage of the national population that was not sampled from.
The PDF specified that stratified sampling was used, which greatly
contributes greatly to the increase in precision
of the findings from the survey and generally leads to a sample that better
represents the population than a simple random sampling.
However, it was unclear to the readers what
characteristics or attributes were used to divide the population into strata.
Since it was stated later in the PDF that the survey wished to obtain
"district-level data for planning purposed" [@citeDHS], it should be safe to
assume that the strata were constructed based on geographical locations.
It is also worth noting that the survey included men from age 15 to 54 while
only including women from age 15 to 49. A sufficient justification was not
found for this discrepancy and it may have an impact on the accuracy of the
findings.

According to the DHS report [@citeDHS], the survey questions can be divided
into 14 categories. Of those 14, the following subset of topic is related
to the focus of this paper:

* Background characteristics such as age and education
* Knowledge and use of family planning methods.

The surveys questions were originally constructed fully in English before being
translated into various local languages, and the wording of the questions
were revised several times by local pretest teams before being sent out, 
ensuring that there will not be any inaccuracies or awkward wording present due
to the language barrier.
[@citeDHS]. This is especially important due to the sensitive nature of the
topics asked in the surveys, and helps in making sure that as many
participants answer honestly as possible.

## Dataset Parsing and Cleaning

The raw dataset is parsed using the package `pdftools` [@citePDF]
and the statistical programming language R [@citeR] from 
Table 10.14.1 and Table 10.14.2 on page 170 and 171 of the PDF respectively 
[@citeDHS]. Two tables are parsed instead of one because the tables each present
data on only one gender. Therefore a dataset that combines data from both
genders in order to provide a more accurate analysis. As such,
a new variable, `gender`, is constructed to help distinguish the data between
female and male participants. Additionally, there is an issue in that the rows
of the tables corresponded to different variables; for example, some rows 
contained data for certain age groups while other rows contained data for 
different marital statuses. To simplify the analysis process, only the rows 
pertaining to age groups, education, and provinces were parsed from the PDF.

The dataset is then cleaned using the `janitor` [@citejani] and `dplyr` 
[@citedplyr] package. The `pointblank` [@citePB] package is used to set 
up validation tests for the class and the content of the datasets.

The final datasets---clean_data_age.csv, cleaned_data_province.csv
and cleaned_data_education.csv---showcased
in Table \@ref(tab:showcase1), Table \@ref(tab:showcase2) and 
Table \@ref(tab:showcase3) respectively,
contains the information about the same variables in every column except the 
first, which is the column that denotes either the age, province or education. 
The purpose of the other columns are explained in the DHS report [@citeDHS],
summarized as follows:

* gender: male or female
* know_about_condoms: percentage of participants that know about condoms
* public_sector: percentage of participants that cited government-run health
services as their primary source for obtaining condoms
* private_medical_sector: percentage of participants that cited private medical
sources as their primary way for obtaining condoms
* private_pharmacy: percentage of participants that cited private pharmacies as
their primary source for obtaining condoms
* shop: percentage of participants that cited commercial shops as their primary
source for obtaining condoms
* cbd_agent: percentage of participants that cited community-based distribution
agents as their primary source for obtaining condoms
* friends_and_relatives: percentage of participants that cited their friends and
relatives as their primary source for obtaining condoms
* other_sources: percentage of participants that cited other sources as their
primary way for obtaining condoms
* dont_know_a_source: percentage of participants that do not know a source for
obtaining condoms
* number_of_people: number of participants that belong in each category

## Preliminary Analysis

Table \@ref(tab:showcase1) shows that an overwhelming majority of surveyees
know about condoms, with all percentages well over 90%. For women, the 
percentage of surveyees that know about condoms are relatively lower in age
groups 15-19 and 40-49, though there is not a similar trend for men, as more
than 97% of men know about condoms in all age groups surveyed. This difference
could be due to the fact that condom is a male-contraceptive and is thus less
advertised to women. Similarly, Table \@ref(tab:showcase1) shows that a larger
percentage of men know about condoms than women in every single province
survyed, though this difference is minuscule.

```{r showcase1, echo=FALSE, warning=FALSE, message=FALSE}
# Read in the dataset
kenya_condom_age <-
  read_csv(here::here("outputs/data/cleaned_data_age.csv"))

# Create a table that showcases the age dataset
kenya_condom_age |> 
  select(age, gender, know_about_condoms ,public_sector, 
         private_medical_sector) |>
  kable(
    caption = "First 5 columns on percentage of participants, categorized by
    age groups, that know about 
    and/or cite a specific source for condoms, or do not know about condoms",
    col.names = c("Age","Gender","Know About Condoms","Public Sector",
                  "Private Medical Sector"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

```{r showcase2, echo=FALSE, warning=FALSE, message=FALSE}
# Read in the dataset
kenya_condom_province <-
  read_csv(here::here("outputs/data/cleaned_data_province.csv"))

# Create a table that showcases the province dataset
kenya_condom_province |> 
  select(province, gender, know_about_condoms ,public_sector, 
         private_medical_sector) |>
  kable(
    caption = "First 5 columns on percentage of participants, categorized by 
    provinces, that know about 
    and/or cite a specific source for condoms, or do not know about condoms",
    col.names = c("Province","Gender","Know About Condoms","Public Sector",
                  "Private Medical Sector"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

```{r showcase3, echo=FALSE, warning=FALSE, message=FALSE}
# Read in the dataset
kenya_condom_education <-
  read_csv(here::here("outputs/data/cleaned_data_education.csv"))

# Create a table that showcases the education dataset
kenya_condom_education |> 
  select(education, gender, know_about_condoms, public_sector, 
         private_medical_sector) |>
  kable(
    caption = "First 5 columns on percentage of participants, categorized by 
    education level, that know about 
    and/or cite a specific source for condoms, or do not know about condoms",
    col.names = c("Education","Gender","Know About Condoms","Public Sector",
                  "Private Medical Sector"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

The datasets also show that there are more than twice the number of female 
participants than male participants. Note that according to Faria [@citeStati],
the gender ratio in Kenya in 2000 is about 98.6 males per 100 females, meaning
that there is no significant numerical difference between genders in Kenya.
Therefore, the unequal sample size in the dataset could lead to unequal
variances between the male and female samples and would negatively affect the
results of any tests that require the assumption of equal variances.

\newpage

## Knowledge of a source for condom: Age Groups

```{r graph, fig.cap="Percentage of Surveyee Without Knowledge of A Source for Condom versus Age Groups", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_age %>%
  ggplot(aes(x = age, y = dont_know_a_source, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Don't know a source for condom (%)",
       x = "Age Group")
```

We can observe from Figure \@ref(fig:graph) that there is a substantially higher
percentage of women who possess no knowledge of ways to obtain condoms
In all age groups, there are on average twice as many women who do not know 
a source to obtain condoms compared to men. This difference is much more
drastic in the younger population (age 15-19).

Note that the female age group of 50-54 was not included in the sample, thus
leaving no way for us to compare the difference in percentage for that specific
age group.

## Knowledge of a source for condom: Geographical Location

```{r graph2, fig.cap="Percentage of Surveyee Without Knowledge of A Source for Condom versus Provinces", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_province %>%
  ggplot(aes(x = province, y = dont_know_a_source, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Don't know a source for condom (%)",
       x = "Province")
```

Figure \@ref(fig:graph2) plots the percentage of male and female
surveyees without knowledge on a source for condoms in each province 
surveyed and in total.

Similar to the trend shown in Figure \@ref(fig:graph), the difference in
percentage between female and male participants are at the minimum 10%, with
women being far more likely to know no source for condoms.

According to Table 2.4 in the Kenya Population and Housing Census in 2019 
[@citeKPHC], Nairobi, the capital city of Kenya, has a population density of
6247 personnel per square kilometer, dwarfing any other county or province in
Kenya. One hypothesis is that this level of population density and urbanization 
may be a reason as to why the gap between female and male knowledge on condom 
sources is relatively smaller in Nairobi. However, Nyanza, a province
where the population density of its counties range from 393 to 958 personnel
per square kilometer, has a difference in female and male knowledge
on condom sources very similar to Nairobi's.

## Knowledge of a source for condoms: Education Level

```{r graph3, fig.cap="Percentage of Surveyee Without Knowledge of A Source for Condom versus Education Level", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_education %>%
  ggplot(aes(x = education, y = dont_know_a_source, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Don't know a source for condom (%)",
       x = "Education")
```

Figure \@ref(fig:graph3) shows a trend that is similar to the previous two;
a higher percentage of women do not know a source for condoms compared to men.
A notable outlier is when there is a complete lack of education: 
Both female and male surveyees without any education have nearly identical 
level of ignorance regarding ways to obtain condoms.

\newpage

# Results

The graphs in the Data section have demonstrated that a significantly higher
percentage of women in Kenya have no knowledge on a source to obtain condoms;
the difference in percentage ranges from 28.8% to 12.2% depending on the
age group, and on average, the difference in percentage of women and men
who have no konwledge on a source to obtain condoms is 15.1%.

## Population density and knowledge on condoms

As shown in Figure \@ref(fig:graph2), the difference in ignorance of condom
sources between women and men vary by a significant amount between provinces.
The initial hypothesis presented in this paper is that the difference could be
linked to the population density in each province. However, after reviewing
the Kenya Population Census [@citeKPHC], no apparent pattern is found. Some
provinces with relatively massive population density such as Nairobi have a 
smaller difference in condom source ignorance as hypothesized to be due to its 
greater urbanization. However, other provinces that contain counties with
population density comparable to Nairobi, such as the Coast province, have
a much large difference in condom source ignorance between men and women:
Mombasa,
a county in the Coast province, has the second largest population density
at 5495 personnel per square kilometer, yet the overall gap between
female and male knowledge on condom sources is still relatively large in
the Coast province. On the other hand, Nyanza, a province
where the population density of its counties range from 393 to 958 personnel
per square kilometer, has a difference in female and male knowledge
on condom sources very similar to Nairobi's.
It is unclear as to whether population density plays an
important role in determining the region's ignorance of sources to obtain
condoms.

## Age Group and knowledge on condoms

Figure \@ref(fig:graph) shows that lack of knowledge on a source for condoms
is much higher in the younger age group (age 15 to 19), decreases in older
age groups, and once ago rises in the oldest age groups (age 40 to 49 and
age 50 to 54).

In general, the disparity between percentage
of women and men that do not know a source for condoms remains largely
unaffected by age groups, though is worth noting however that younger surveyees
(people in the age of 15 to 19) have a relatively higher difference in this
regard.
In total, the percentage of women that do not know of a source 
for condoms are 15.1% higher than men.

## Education Level and knowledge on condoms

As demonstrated in Figure \@ref(fig:graph3), a staggeringly high percentage
of women and men with no education have no knowledge on where to obtain
condoms. 
The graph also shows that receiving a higher level of
education correlates to an overall decrease in lack of knowledge on sources for
condom supply in
both genders. However, the difference in condom source ignorance between
women and men seem to not be correlated to education level, as the difference
in condom source ignorance between genders is lower in both the 'No Education'
and 'Secondary+' levels compared to the 'Primary Incomplete' and
'Primary Complete' levels.

```{r graph4, fig.cap="Percentage of Surveyees Citing Public Sector as Primary Source for Condom versus Education Level", echo = FALSE, fig.width=8, fig.height=4}
kenya_condom_education %>%
  ggplot(aes(x = education, y = public_sector, color = gender)) +
  geom_point(size = 4) +
  theme_minimal() +
  labs(y = "Cited Public Sector as Primary Source (%)",
       x = "Education")
```

Another important thing to note is shown in Figure \@ref(fig:graph4), as a larger
percentage of both men and women in Kenya cite government-funded public services
as their primary source of condom supply as their education levels increase.
This suggests that an increase in public sector advertisement campaign targeted
towards poorly educated citizens could increase usage rate of condoms.

# Discussion

## Level of Variance in Population Density

As discussed in the Results section, we seemingly cannot establish a
relationship between population density of a province and the difference in
condom source ignorance between its female and male residents. The reasoning
is that provinces that contain counties with similar levels of population
density have very difference disparities in the percentage of women and men that
know where to obtain condoms. However, it is important to note that each
province is sectioned into different numbers of counties. A possible connection
that was not analyzed in this paper is the hypothesis that the aforementioned
disparities were caused by the level of variance in population density among
the counties for each province. For example, according to the Kenya Population
Census [@citeKPHC], Nyanza, a province
where the population density of its counties range from 393 to 958 personnel
per square kilometer, has a difference in female and male knowledge
on condom sources very similar to that of the Nairobi province. On the other
hand, the Rift Valley province contains counties with population density 
ranging from 14 to 397 personnel per square kilometer, and the Eastern province
contains counties with population density ranging from 6 to 236 personnel per
square kilometer. In these two provinces which have relatively lower variance in
its counties' population densities, the difference in percentage of women
and men that know sources for condoms are much larger compared to Nyanza, a
province with a higher variance in its counties' population densities. There is
a possibility of correlation in here, and this
direction could prove to be an interesting add-on or extension of this paper.

## Higher percentage of women with no knowledge of condom sources on average

Across all the tables and graphs presented in this paper, it is apparent that
on average, a significantly higher percentage of women have no knowledge
sources for condoms. It is unclear as to why this disparity exists. One possible
reasoning is that condom is a male-contraceptive and thus less advertised to
women. This suggests that creating more condom advertisements targeted at women
in Kenya could potentially lead to an increase in condom usage as contraceptive
method.

## Higher level of education leads to less ignorance on sources of condom supply

Figure \@ref(fig:graph3) shows that higher levels of education seemingly
correlates with a sharp decrease in ignorance of sources of condom supply.
While it may be difficult to increase the country's educational findings and
quality on a national scale, it could be beneficial to set up clinics or
government-sponsored services that inform the less educated population about
sources of condom supply, especially given what is presented in
Figure \@ref(fig:graph4).


## Limitations

### Unequal sampling size between genders

As discussed in the beginning of the Data section, in the report conducted by
the DHS Program that is used to extract the raw data for this paper from, there
are more than twice the number of female surveyees than male surveyees, yet,
according to Faria [@citeStati],
the gender ratio in Kenya in 2000 is about 98.6 males per 100 females, meaning
that there is no significant numerical difference between genders in Kenya.
Therefore, there is no feasible justification for this difference in sample
size between genders. This disadvantage could negatively affect the accuracy
of any tests based on the assumption of equal variances.

### Inexplicable lack of data

As showcased in Figure \@ref(fig:graph), there is a lack of data for women in
the age group of 50 to 54 and we could not locate an explanation for it in the
DHS Program report. It could be that there were simply not enough female
surveyees in the age group of 50 to 54; While it was stated in the DHS Program
report [@citeDHS] that it used stratified sampling, the report did not specify
which characteristic the sample was stratified on, leaving no way for us to
figure out the reasoning behind this discrepancy.

### Omission of certain counties and estimation for certain counties

The survey used by the DHS Program was distributed in nearly all districts in
Kenya. While the total population of the districts not included in the survey
only amounts to less than four percent of the country's population, it is still
a substantial percentage of the national population that was not sampled from.

Additionally, the DHS Program report [@citeDHS] noted that due to a drastic
increase in number of counties in the country in the few years prior to the
publication of the report, values for certain variables for some rural counties
were estimated instead. One of the reasons for doing so, as stated in the DHS
Program report, was that these districts were included in the previous two
DHS Program reports of the same nature on Kenya, and thus reliable estimates
could be achieved. It is unclear as to how much these estimates deviate from
the true data or how much effect this has on the overall dataset, but it is
nevertheless a potential source of error that sadly cannot be remedied in the
scope of this paper alone.


\newpage

\appendix

# Appendix {-}

## Datasheet for the Dataset

Extract of the questions from @gebru2021datasheets

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of condom usage for men and women in Kenya. The raw data used to create this dataset was presented in a PDF format obtained from the 1998 DHS Program report on Kenya [@citeDHS] and thus parsing was required to convert the raw data into a usable format. The original purpose of the raw data was to help inform local policy makers on the subject of family planning and the use of contraception.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The raw data used for the dataset was created by the Demographic and Health Surveys Program, a program supported by the American organization USAID. The parsed dataset was created by Tian Yi Zhang, a student at the University of Toronto.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The raw data used for th dataset was funded by the American organizatino USAID.
4. *Any other comments?*
    - None.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances are respondents to a survey constructed by the DHS Program in 1998 which was distributed to a sample of the citizens from age 15-54 in Kenya.
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 6581 female respondents and 2962 male respondents.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of instances. It is intended to be a stratified sample of the entire population of Kenya,
	presumed stratified based on the geographical location (i.e. county) of the respondents. Estimates of instances were
	used for the rural areas in the following 15 districts: Bungoma, Kakamega, Kericho, Kilifi, Kisii, Machakos, Meru, Murang'a, Nakuru, Nandi, Nyeri, Siaya, South Nyanza, Taita-Taveta, Uasin Gishu, Nairobi, and Mombasa. According to @citeDHS, estimates were partially utilized because the districts were considered large in their respective provinces and had been surveyed in the two Kenya DHS reports prior to this one.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	-  The first column in each dataset denotes the feature by which the data is being categorized. The gender variable denotes the gender of the respondent, the know_about_condoms variable denotes the percentage of respondents that know about condoms. The rest of the variables, aside from number_of_people, denote the percentage of respondents that cited each variable as their primary source of condom supply.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- the gender is either male or female, the other variables are percentage-based.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- there are no data for the female age group of 50-54 in the raw data used for the dataset. An explanation was unable to be found in the Kenya DHS report.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- The variables that denote the percentage of respondents that cite said variables as their primary source of condom supply (or, does not know a source of condom supply) adds up to 100%.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- None.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The sample size is unequal for female and male respondents despite the ratio of men to women in Kenya being 98.6 to 100, according to Faria [@citeStati]. There is no explanation provided in the Kenya DHS report, but this unequal sample size does negatively affect the assumption of equal variances.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- As mentioned before, the datasets are parsed from Table 10.14.1 and Table 10.14.2 on page 170 and 171 of the Kenya DHS report PDF. [@citeDHS]
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- Unknown to the authors of the datasheet. However, seeing that the Kenya DHS report PDF is publicly available for download on the DHS Program's official website, one could safely assume that no confidential data is included.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The dataset does not contain any offensive or insulting data.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The datasets are split by age, gender, education level, and provinces. These splits are provided by the raw data obtained from the Kenya DHS report.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- It is entirely impossible to identify individuals from the dataset as the individual questionnaires submitted by each respondent are present in neither the original Kenya DHS Program or the converted datasets.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The datasets do not contain data that might be considered sensitive in any way.
16. *Any other comments?*
	- None.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was collected through a questionnaire distributed to the respondents by the Kenya DHS program.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- As mentioned previously, a questionnaire was created and distributed. Any programs used to record the information obtained from the said questionnaire are entirely unknown to the author of the datasheet.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- According to the Kenya DHS report [@citeDHS], stratified sampling was used, though the specific characteristic by which the strata were constructed are not mentioned in the original report.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Unknown to the author of the datasheet.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Unknown to the author of the datasheet.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Unknown to the author of the datasheet.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The raw data was collected by the Kenya DHS Program through a questionnaire, the methods through which the data is recorded by them is entirely unknown to the author of the datasheet.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Unknown to the author of the datasheet.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Unknown to the author of the datasheet.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- N/A.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Unknown to the author of the datasheet.
12. *Any other comments?*
	- None.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Instances in the data regarding area of residence (rural vs. urban) and marital status (never married, formerly married, currently married) were removed in the final datasets.
	- Any preprocessing of raw data in the Kenya DHS Program are entirely unknown to the author of the datasheet.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The removed instances in the datasets are not saved.
	- Any preprocessing of raw data in the Kenya DHS Program are entirely unknown to the author of the datasheet.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- statistical programming language R [@citeR] was used to preprocess the datasets.
	- Any softwares used to preprocess the raw data in the Kenya DHS Program are entirely unknown to the author of the datasheet.
4. *Any other comments?*
	- None.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- At the time of writing this, only this paper has used the converted datasets
	- Any other conversion and subsequent usage of the original raw data from the Kenya DHS Program are entirely unknown to the author of this datasheet.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The repository for this paper, which uses the datasets, are available at https://github.com/zhan7818/kenya-condom-knowledge
	- Any other repositories for other conversions and subsequent usage of the original raw data from the Kenya DHS Program are entirely unknown to the author of this datasheet. 
3. *What (other) tasks could the dataset be used for?*
	- The datasets could be used to modeling or finding relationship between various primary sources of condom supply.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- There is a minuscule risk for harm: The original data presented by Kenya DHS Program was already publicly available for download and contained minimal sensitive information, thus making the converted datasets safe for future uses.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The datasets should not be used in an effort to discriminate against individuals in Kenya.
6. *Any other comments?*
	- None.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Since there datasets are publicly available on the internet, yes.
	- The original raw data presented in the Kenya DHS report are also publicly available for download on the internet.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The datasets are distributed on Tian Yi Zhang's github page, along with this paper: https://github.com/zhan7818/kenya-condom-knowledge.
	- The original raw data presented by Kenya DHS Program is available at https://dhsprogram.com/publications/publication-fr102-dhs-final-reports.cfm?csSearch=456440_1
3. *When will the dataset be distributed?*
  - The datasets used in this paper are distributed in 2022.
	- The original raw data presented by Kenya DHS Program was published in 1998.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The datasets are distributed under a MIT license.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No restrictions are placed on the datasets converted in this paper.
	- Third party restrictions placed on the original raw data presented in the Kenya DHS report are entirely unknown to the author of the datasheet.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- Unknown to the author of the datasheet.
7. *Any other comments?*
	- None.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Tian Yi Zhang is hosting the converted datasets
	- The original raw data presented in the Kenya DHS report is being hosted by the DHS Program on their official website.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The creator of the datasets, Tian Yi Zhang, can be contacted at tianyi.zhang6546@gmail.com.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- As of writing this datasheet, no explicit erratum have been spotted.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Any updates will be posted on the github page used to host this paper which include the datasets.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the datasets (if there will be any) will be kept as a record on github.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- One should contact the Kenya DHS program responsible for collecting and presenting the raw data used to convert the datasets in this case.
8. *Any other comments?*
	- None.

\newpage

# References


